\vspace{-2cm}A generative model for urban firm networks

### 2020-09-03 main.tex
Update on Overleaf.

\cite{derudder2018central}
\cite{storme2019introducing} cities firms interactions

@@

We run a specific experiment to study the impact of urban hierarchy on firms dynamics. Rank-size law in cities is a central stylized fact to urban theories, despite the discussions on how to estimate the power-law exponent, its actual values \cite{cottineau2017metazipf} and how its depends on the definition of cities considered \cite{corral2020truncated}. In that particular context, understanding how this parameter can impact urban dynamics within artificial systems of cities in which it can be modified to extreme values not observed in real systems, should inform on underlying processes. % too abstract: clarify why hypothetical systems of cities bring info on real ones \cite{raimbault2019space}
We change the initial hierarchy $\alpha$ from 0.2 to 2.0 with a step of 0.1, and also vary interaction range $d_0$.

%%%%%%%%%%%%%
\begin{figure}
    \begin{center}
        %\includegraphics[width=\linewidth]{figures/Fig7.png}
    \end{center}
    \caption{\textbf{Impact of urban hierarchy.}\label{fig:fig7}}
\end{figure}
%%%%%%%%%%%%%

>>>>

%is it something you want to add?
%\cite{derudder2018central}
%\cite{storme2019introducing} cities firms interactions

@@

We run a specific experiment to study the impact of urban hierarchy on firms dynamics. Rank-size law in cities is a central stylized fact to urban theories, despite the discussions on how to estimate the power-law exponent, its actual values \cite{cottineau2017metazipf} and how its depends on the definition of cities considered \cite{corral2020truncated}. In that particular context, understanding how this parameter can impact urban dynamics within artificial systems of cities in which it can be modified to extreme values not observed in real systems, should inform on underlying processes \cite{raimbault2019space}. We change the initial hierarchy $\alpha$ from 0.5 to 2.0 with a step of 0.1, and also vary the interaction range $d_0$.

%%%%%%%%%%%%%
\begin{figure}
    \begin{center}
        \includegraphics[width=\linewidth]{figures/Fig7.png}
    \end{center}
    \caption{\textbf{Impact of urban hierarchy.}\label{fig:fig7}}
\end{figure}
%%%%%%%%%%%%%
